---
title: "Data Wrangling Tutorial"
author: "Megan Willis & Kyle Goulart"
output:
    learnr::tutorial:
          theme: "journal"
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(schrute)
library(tidyverse)
library(dplyr)
library(ggthemes)
```

```{r, include = FALSE}
#converting season and episode to numeric
theoffice$season<-as.numeric(theoffice$season)
theoffice$episode<-as.numeric(theoffice$episode)
```
## Intro to Data Wrangling: *The Office (U.S.)* Edition
Data wrangling is a process that takes datasets and transforms them into a form that is more helpful for the task at hand. Any of all parts of the data can be manipulated, renamed, and even removed. In R, there are many functions that can be used on a dataset to complete the process of data wrangling. 

## The Data Set
In this tutorial, we will be using **theoffice** dataset found within the `schrute` package, which contains the season, episode number and name, characters and their lines (in order), episode ratings, as well as other pieces of information pertaining to the show.

## Overview of Functions

**The** `select( )` **function** is used to choose which *columns* you would like to include. You can also use this function to remove columns. The order in which you include the columns as arguments are the order they will appear in your new dataset. Ex: select(season, episode_name)

**The** `filter( )` **function** is used to select which *rows* you would like to include. To select a single parameter, use the '==' operator. To select multiple parameters, use an '%in%', along with a vector of the parameters (vector format: c(x1,x2,...)). Ex: filter(season == 5) or filter(season %in% c(5,6))

**The** `mutate( )` **function** changes the dataset. You can use this function to add new columns based on existing columns. Ex: mutate(bmi = weight/height^2)

**The** `arrange( )` **function** arranges *rows*. It defaults to arranging the data in ascending order, but can also be written to arrange in descending order, which is sometimes more helpful. You just select the column you would like to arrange by. Ex: arrange(desc(n))

**The** `rename( )` **function** does exactly that: renames *columns*(variables). Ex: rename(rating = imdb_rating)

**The** `summarize( )` **function** creates a data set based on a specific summary statistic. For example, if you wanted the mean of a particular value, the new data set would report the data based on the mean values found. This function is often used alongside group_by(). Ex: summarize(x_mean = mean(x))

**The** `group_by( )` **function** groups specified parts of the data. This *must* be followed by another function, such as summarize( ). When used together, you can group by a specific parameter and then calculate the summary statistics for each subgroup. Ex: group_by(season, episode_name)

**The** `top_n( )` **function** is used to report the top numbers for a specific variable or value. You can specify how many values you would like reported in the table within the function. Ex: top_n(x,10)

**The** `count( )` **function** is used to count up a number of objects. It can be used in place of the summarize() function for counting purposes. The argument sort = TRUE can be added to replace the arrange(desc()) function and argument as well. Ex: count(num_episodes = n(), sort = TRUE)

### Useful Operators to Know

There are a few different operators that will be good to know before getting started. Mentioned in the `filter( )` section above, the **==** tests for *equality* and is commonly used for a *single* parameter. The **%in%** operator also tests for *equality*, but for *multiple* parameters in the vector that follows. 

The **pipe operator (%>%)** is extremely prevalent in the world of data wrangling. The pipe operator allows you to move seamlessly from operation to operation, forming a *pipeline*. It pipes the output of one operation to the input of the next operation, streamlining multiple operations performed on a single dataset, instead of doing each individually. You will see this operator in action throughout the remainder of the tutorial.

## Practice with select( ) & filter( )

**Create dataset for season 1**
```{r example_code, exercise = TRUE}
season1 = theoffice %>%   #creates a new dataset season1 from theoffice dataset
  filter(season == 1) %>%   #select all ROWS pertaining to season 1
  select(episode, episode_name, imdb_rating) %>%   #select the COLUMNS to include in the new dataset
  group_by(episode, episode_name) %>%   #group the dataset by episode and episode name
  summarize(imdb_rating = paste(unique(imdb_rating),
                                collapse = ", "))   #summarize by the groups specified in group_by(), and creates a new 
                                                    #imdb_rating column by collapsing the data into one row per episode
head(season1, 5)   #displays the first 5 rows in the dataset
```

**Practice!**
Create a dataset like the one above, but for season 2. Report a table including the following columns: episode, episode_name, and imdb_rating. Fill in the correct information in the `filter( )` and `select( )` lines.
```{r practice1, exercise = TRUE}
season2 = theoffice %>% 
  filter( ) %>% 
  select( ) %>% 
  group_by(episode, episode_name) %>% 
  summarize(imdb_rating = paste(unique(imdb_rating), collapse = ", "))
head(season2, 5)
```

## Practice with group_by( ) & count( )

Run the following code to calculate the average rating for each season, along with the number of episodes in each season
```{r season_avg, exercise = TRUE}
seasons_avg = theoffice %>%   #creates a new dataset for the average rating per season
  select(season, episode, imdb_rating) %>%   #select the COLUMNS to use to create the new dataset
  group_by(season) %>%   #group the dataset by season
  mutate(avg_rating = mean(imdb_rating, na.rm = TRUE))%>%   #create a new COLUMN called avg_rating by calculating the 
                                                            #mean for each season
  group_by(season, episode, avg_rating) %>%   #group the dataset by season, episode and the new column avg_rating
  count(num_episodes = n()) %>%   #counts number of episodes per season 
                                  #**Note: inaccurate due to multiple rows per season in original dataset 
  group_by(season, avg_rating) %>%   #group by season and avg_rating again
  count(num_episodes = n()) %>%   #counts the number of episodes per season in new COLUMN 
                                  #called num_episodes
  select(season, num_episodes, avg_rating)  #reorder selected columns

seasons_avg$avg_rating = round(seasons_avg$avg_rating, 2)   #Rounds the avg_rating to one 
                                                            #decimal place
head(seasons_avg, 9)  #displays first 9 rows of dataset
```

```{r seasonsforplot, exercise = FALSE}
#saved dataset for ggplot
seasons_avg = theoffice %>% 
  select(season, episode, imdb_rating) %>% 
  group_by(season) %>% 
  mutate(avg_rating = mean(imdb_rating, na.rm = TRUE))%>% 
  group_by(season, episode, avg_rating) %>% 
  count(num_episodes = n()) %>% 
  group_by(season, avg_rating) %>% 
  count(num_episodes = n()) %>% 
  select(season, num_episodes, avg_rating)

seasons_avg$avg_rating = round(seasons_avg$avg_rating, 2)
```


Now, using what you've learned about the `filter( )` function, create a dataset with the average rating and number of episodes for seasons 3 and 8. Also, fill in code for the `select( )`, `group_by( )`, and `count( )` lines. Use the code in the example above as a reference.
```{r season_avg_3_8, exercise = TRUE}
seasons_avg_3_8 = theoffice %>% 
  filter( ) %>% 
  select( ) %>% 
  group_by( ) %>% 
  mutate(avg_rating = mean(imdb_rating, na.rm = TRUE))%>% 
  group_by(season, episode, avg_rating) %>% 
  count(num_episodes = ) %>% 
  group_by(season, avg_rating) %>% 
  count(num_episodes = ) %>% 
  select(season, num_episodes, avg_rating)
head(seasons_avg_3_8, 2)
```

## Data In Action

Now take a look at this data graphic using the new **seasons_avg** dataset we created earlier!
```{r plot, warning = FALSE, exercise = TRUE}
ggplot(data = seasons_avg, aes(x = reorder(season, -season), y = avg_rating)) + 
  geom_col(fill = "lightgoldenrod2", color = "lightgoldenrod4") + 
  labs(title = "Average IMDb Rating Per Season", subtitle = "The Office (U.S.)", x = "", y = "Average Rating") + 
  theme_economist_white() + 
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) + 
  scale_y_continuous(breaks = seq(0,9, by = 1.0), labels = c(0.0, 1.0, 2.0, 3.0, 4.0, 5.0, 6.0, 7.0, 8.0, 9.0)) + 
  annotate("text", x = 9, y = 1, label = "Season 1", fontface = "bold", size = 5) + 
  annotate("text", x = 8, y = 1, label = "Season 2", fontface = "bold", size = 5) +
  annotate("text", x = 7, y = 1, label = "Season 3", fontface = "bold", size = 5) +
  annotate("text", x = 6, y = 1, label = "Season 4", fontface = "bold", size = 5) +
  annotate("text", x = 5, y = 1, label = "Season 5", fontface = "bold", size = 5) +
  annotate("text", x = 4, y = 1, label = "Season 6", fontface = "bold", size = 5) +
  annotate("text", x = 3, y = 1, label = "Season 7", fontface = "bold", size = 5) +
  annotate("text", x = 2, y = 1, label = "Season 8", fontface = "bold", size = 5) +
  annotate("text", x = 1, y = 1, label = "Season 9", fontface = "bold", size = 5) + 
  geom_text(aes(label = avg_rating), vjust = .5, hjust = 1.5) + 
  coord_flip()
```

### Background & Conclusions

Looking at this data graphic, it is clear that overall, *The Office (U.S.)* is highly rated among it's viewers. These findings make sense based on the rapport the show possesses. The show aired in 2005, and continued on for 9 seasons, through 2013. Given the continued success, and therefore the continued production, it is reasonable to assume that the average rating season to season was high. Those assumptions are supported by the results displayed in the above plot. As fans of *The Office (U.S.)*, the trend of higher ratings in the early to middle seasons, as well as the final season seem to add up. Personally, our favorite seasons are seasons 3-6, so we fully support the results that show these seasons are highly regarded by fellow fanatics. It is arguably one of the best TV shows of all time! 




















